Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ \smaller \textbf{{Berlin version \YellowPaperVersionNumber}}

### 2022-06-09 Paper.tex
Fix: revert message should be available in the returndata buffer in case a CREATE reverts

We define $\Xi_{\mathtt{ECREC}}$ as a precompiled contract for the elliptic curve digital signature algorithm (ECDSA) public key recovery function (ecrecover).
See Appendix \ref{app:signing} for the definition of the function $\mathtt{ECDSARECOVER}$ and the constant $\mathtt{secp256k1n}$.
We also define $\mathbf{d}$ to be the input data, well-defined for an infinite length by appending zeroes as required.
In the case of an invalid signature, we return no output.

\begin{eqnarray}
\Xi_{\mathtt{ECREC}} &\equiv& \Xi_{\mathtt{PRE}} \quad \text{where:} \\
g_{\mathrm{r}} &=& 3000\\
\lVert \mathbf{o} \rVert &=& \begin{cases} \label{eq:ecrec_precompile_validity}
  0 & \text{if} \quad v \notin \{27, 28\} \,\vee\, r = 0 \,\vee\, r \ge \mathtt{secp256k1n} \,\vee\, s = 0 \,\vee\, s \ge \mathtt{secp256k1n} \\
  0 & \text{if} \quad \mathtt{ECDSARECOVER}(h, v - 27, r, s) = \varnothing\\
  32 & \text{otherwise}
\end{cases}\\
\text{if} \quad \lVert \mathbf{o} \rVert = 32: &&\\
\mathbf{o}[0..11] &=& 0 \\
\mathbf{o}[12..31] &=& \mathtt{KEC}\big(\mathtt{ECDSARECOVER}(h, v - 27, r, s)\big)[12..31] \quad \text{where:}\\
\mathbf{d}[0..(\lVert \hyperlink{I__d}{I_{\mathbf{d}}} \rVert-1)] &=& I_{\mathbf{d}}\\
\mathbf{d}[\lVert I_{\mathbf{d}} \rVert..] &=& (0, 0, ...) \\
h &=& \mathbf{d}[0..31]\\
v &=& \mathbf{d}[32..63]\\
r &=& \mathbf{d}[64..95]\\
s &=& \mathbf{d}[96..127]
\end{eqnarray}

@@

We assume the existence of functions $\mathtt{ECDSAPUBKEY}$, $\mathtt{ECDSASIGN}$ and $\mathtt{ECDSARECOVER}$. These are formally defined in the literature, \eg by \cite{ECDSAcerticom}.
\begin{eqnarray}
\mathtt{ECDSAPUBKEY}(p_{\mathrm{r}} \in \mathbb{B}_{32}) & \equiv & p_{\mathrm{u}} \in \mathbb{B}_{64} \\
\linkdest{ECDSASIGN}\mathtt{ECDSASIGN}(e \in \mathbb{B}_{32}, p_{\mathrm{r}} \in \mathbb{B}_{32}) & \equiv & (v \in \mathbb{B}_{1}, r \in \mathbb{B}_{32}, s \in \mathbb{B}_{32}) \\
\mathtt{ECDSARECOVER}(e \in \mathbb{B}_{32}, v \in \mathbb{B}_{2}, r \in \mathbb{B}_{32}, s \in \mathbb{B}_{32}) & \equiv & p_{\mathrm{u}} \in \mathbb{B}_{64}
\end{eqnarray}

@@

\linkdest{invalidsig}We declare that an ECDSA signature is invalid unless all the following conditions are true:
\begin{align}
0 < \linkdest{r}{r} &< \mathtt{secp256k1n} \\
0 < \linkdest{s}{s} &< \mathtt{secp256k1n} \div 2 + 1 \\
\hyperlink{v}{v} &\in \{0,1\}
\end{align}
where:
\begin{align}
\mathtt{secp256k1n} &= 115792089237316195423570985008687907852837564279074904382605163141518161494337
%\mathtt{secp256k1p} &= 2^{256} - 2^{32} - 977\\
\end{align}
Note that this restriction on $s$ is more stringent than restriction \ref{eq:ecrec_precompile_validity} in the ECREC precompile; see EIP-2 by \cite{EIP-2} for more detail.

@@

&&&& $\boldsymbol{\mu}'_{\mathbf{o}} \equiv ()$ \\

>>>>

We define $\Xi_{\mathtt{ECREC}}$ as a precompiled contract for the elliptic curve digital signature algorithm (ECDSA) public key recovery function (ecrecover). See Appendix \ref{app:signing} for the definition of the function $\mathtt{ECDSARECOVER}$. We also define $\mathbf{d}$ to be the input data, well-defined for an infinite length by appending zeroes as required. In the case of an invalid signature ($\mathtt{ECDSARECOVER}(h, v, r, s) = \varnothing$), we return no output.

\begin{eqnarray}
\Xi_{\mathtt{ECREC}} &\equiv& \Xi_{\mathtt{PRE}} \quad \text{where:} \\
g_{\mathrm{r}} &=& 3000\\
\lVert \mathbf{o} \rVert &=& \begin{cases} 0 & \text{if} \quad \mathtt{v} \neq 27 \wedge \mathtt{v} \neq 28 \\ 0 & \text{if} \quad \mathtt{ECDSARECOVER}(h, v - 27, r, s) = \varnothing\\ 32 & \text{otherwise} \end{cases}\\
\text{if} \quad \lVert \mathbf{o} \rVert = 32: &&\\
\mathbf{o}[0..11] &=& 0 \\
\mathbf{o}[12..31] &=& \mathtt{KEC}\big(\mathtt{ECDSARECOVER}(h, v - 27, r, s)\big)[12..31] \quad \text{where:}\\
\mathbf{d}[0..(\lVert \hyperlink{I__d}{I_{\mathbf{d}}} \rVert-1)] &=& I_{\mathbf{d}}\\
\mathbf{d}[\lVert I_{\mathbf{d}} \rVert..] &=& (0, 0, ...) \\
h &=& \mathbf{d}[0..31]\\
v &=& \mathbf{d}[32..63]\\
r &=& \mathbf{d}[64..95]\\
s &=& \mathbf{d}[96..127]
\end{eqnarray}

@@

We assume the existence of functions $\mathtt{ECDSAPUBKEY}$, $\mathtt{ECDSASIGN}$ and $\mathtt{ECDSARECOVER}$. These are formally defined in the literature, \eg by \cite{ECDSAcerticom}.
\begin{eqnarray}
\mathtt{ECDSAPUBKEY}(p_{\mathrm{r}} \in \mathbb{B}_{32}) & \equiv & p_{\mathrm{u}} \in \mathbb{B}_{64} \\
\linkdest{ECDSASIGN}\mathtt{ECDSASIGN}(e \in \mathbb{B}_{32}, p_{\mathrm{r}} \in \mathbb{B}_{32}) & \equiv & (v \in \mathbb{B}_{1}, r \in \mathbb{B}_{32}, s \in \mathbb{B}_{32}) \\
\mathtt{ECDSARECOVER}(e \in \mathbb{B}_{32}, v \in \mathbb{B}_{1}, r \in \mathbb{B}_{32}, s \in \mathbb{B}_{32}) & \equiv & p_{\mathrm{u}} \in \mathbb{B}_{64}
\end{eqnarray}

@@

\linkdest{invalidsig}We declare that an ECDSA signature is invalid unless all the following conditions are true:
\begin{align}
0 < \linkdest{r}{r} &< \mathtt{secp256k1n} \\
0 < \linkdest{s}{s} &< \mathtt{secp256k1n} \div 2 + 1 \\
\hyperlink{v}{v} &\in \{0,1\}
\end{align}
where:
\begin{align}
\mathtt{secp256k1n} &= 115792089237316195423570985008687907852837564279074904382605163141518161494337
%\mathtt{secp256k1p} &= 2^{256} - 2^{32} - 977\\
\end{align}

@@

&&&& $\boldsymbol{\mu}'_{\mathbf{o}} \equiv \begin{cases}
() & \text{if} \quad z = 1 \\
\mathbf{o} & \text{otherwise}
